Manuscript_Github_Pchabaudi_pir

### 2022-07-26 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Summary table of top GO terms for Cellular Components

#Make a topGOdata object 
GOdata <- new("topGOdata", 
              ontology = "CC", 
              geneSel = function(x){x == 1},
              allGenes = z_max_diff.list$`0`,
              annot = annFUN.gene2GO, 
              gene2GO = go_annotation)

>>>>

#Make a topGOdata object 
GOdata <- new("topGOdata", 
              ontology = "CC", 
              geneSel = function(x){x == 1},
              allGenes = z_max_diff.list$`0`,
              annot = annFUN.gene2GO, 
              gene2GO = go_annotation)
resultFis <- runTest(GOdata, algorithm = "classic", statistic = "fisher")
hist(score(resultFis), 50, xlab = "p-values")
GenTable(GOdata, 
         classic = resultFis, 
         orderBy = "classic", 
         ranksOf = "classic",
         topNodes = 25)
```
